MLH1 data report 

### 2017-09-22 rmd_report.rmd
edits to report, sampling simulations

>>>>

```{r}
dataset <- cbind (idorg,x,y)
attempt <- list()
for (i in 1:6)  {
  attempt[[i]] <- dataset[sample(1:nrow(dataset), 3, replace=FALSE),]

}
attempt[6][[1]][,'idorg']# 6th mini df, the column 'idorg'

# apply functions across dataframe for mice, #create a dataframe from the variables made #isolate data set for mice with enough cells (or find a way to code around the errors)

df_sample_size_test <-  ddply(MLH1_data, .(mouse), function(x) {
#for each mouse in big data set, make samples of different sizes 10 times
              ncell <- length(unique(x$file.name))       
              smpl10 <- mean( sample(x$adj_nMLH1.foci, ncell*0.1, replace=FALSE) )
             # smpl10x10 <- mean( sample(x$adj_nMLH1.foci, ncell*0.1, replace=FALSE) )
              attempt = list()
              for (i in 1:10)  {
                  attempt[[i]] <- dataset[sample(1:nrow(x$adj_nMLH1.foci), 10, replace=FALSE),]
              }
              smple_10x10 = mean(attempt[1:10][[1]][,'adj_nMLH1.foci'])

      data.frame(ncell=ncell, mean10 = smpl10, s10x10 = smple_10x10)
})
attempt[6][[1]][,'idorg']# 6th mini df, the column 'idorg'

PWD_m_example = MLH1_data[MLH1_data$mouse == '10mar15_PWD_m2', ]

dataset <- cbind (idorg,x,y)
 attempt = c()
              for (i in 1:3)  {
                  attempt[[i]] <- sample(PWD_m_example$nMLH1.foci, 10, replace=FALSE)
              }
              smple_10x10 = mean(attempt[1:10][[1]][,'nMLH1.foci'])#col isn't name ... don't need the name

idorg <- c(1,2,3,4,5)
x <- c(14,20,21,16,17)
y <- c(31,21,20,50,13)

#loop below simulates sampling 6 times, from the dataset. a mini df is made out of the samples
#
dataset <- cbind (idorg,x,y)
attempt <- list()
for (i in 1:6)  {
  attempt[[i]] <- dataset[sample(1:nrow(dataset), 3, replace=FALSE),]

}
attempt[6][[1]][,'idorg']# 6th mini df, the column 'idorg'

category_pwr_stat <- ddply(MLH1_data, "category", function(x) {
Nmice <- length( unique(x$mouse) )
mean.count <- mean(x$adj_nMLH1.foci)
sd.count <- sd(x$adj_nMLH1.foci)
cv <- sd.count/mnea.count

ttest.p <- t.test(x$adj_nMLH1.foci, (20), alternative = "two", var.equal=TRUE)$p.value
ttestCI.lowr <- t.test(x$adj_nMLH1.foci, (20), alternative = "two", var.equal=TRUE)$conf.int[1]
ttestCI.upr <- t.test(x$adj_nMLH1.foci, (20), alternative = "two", var.equal=TRUE)$conf.int[2]
ttest.est <- t.test(x$adj_nMLH1.foci, (20), alternative = "two", var.equal=TRUE)$estimate

pwr5mice <- pwr.norm.test(d = (3/sd.count), n = 20, sig.level = 0.05, alternative = "two")$power

data.frame(Nmice=Nmice, cv = cv, ttest=ttest.p, CIlower = ttestCI.lowr, 
           CIupr = ttestCI.upr,
 pwr = pwr5mice, ttest.est=ttest.est)
})
